\documentclass{article}

\usepackage[margin=1in]{geometry}

\begin{document}

		\title{A CONCEPT PAPER ABOUT STRIKES AT MAKERERE UNIVERSITY}
		\author{Author :  TEBERYOWA  JUSTINE }
		
                      \date{Reg no: 15/U/13132/PS}
		\maketitle
	

	\tableofcontents

	
\section{Introduction}
This concept contains collecting data about the causes of the strike in some years like in 2014, 2015 and 2016. It contains different pictures of different strikes happening and videos of the strikes.
The concept will also consider about the solutions to the strike.
It gives quick access to all strikes that are happening at Makerere university.

\subsection{Background}
The data was collected via the televisions, radios, newspapers. This was given by NTV .
On October 20, resident students of Lumumba, Mary Stuart and Complex halls went on strike protesting poor quality of meals served. Led by residents of Lumumba Hall, the angry students poured down all the food they had been served for supper.
In 2014, Makerere University stopped providing meals to government-sponsored students in halls of residence, and outsourced the catering services to private firms. The institution wanted to focus on its core functions of teaching and research.

\subsection{general objective}
To get quick information about the strikes that are happening at makerere university and getting solutions to them which saves time of looking for videos and images of the strike


 \subsection{Limitations}
Getting information  about videos, images of the strike needs internet connection.


\section{literature review}
Getting information about particular causes of the strikes at makerere university, solutions to the strike and uploadig of images and videos

\section{methodology}
Through the use of ODK on the mobile phones, data for the causes of the strike is entered in the form, year of the strike,uploading of the picture of the strike is done, uploading a video, and the form is saved. 
    

\section{Conclusion}
This concept will provide information about the causes of the strikes at makerere university.it will help in resolving issues and getting solutions to the strike. 
  

\end{document}